Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-07 paper/paper.tex
pass on section III

\subsection{Seed JS files\label{sec:seeds}}~We considered in our study test suites
associated with all four JS engines we analyzed
(section~\ref{sec:methodology:engines}). In addition, we mined test
suites from other repositories based on the following criteria:
\begin{itemize}
  \item The project must be an open-source project and at least 1K stars from community.
  \item The repository must have JavaScript tests included.
  \item It does not use external libraries 
\end{itemize}

Figure~\ref{fig:query} illustrates the Github API query\Fix{cite} we
used to find javascript engines projects defined by the keyword "javascript-engine". 
The resulting list includes a total of 33 projects.
A total of \Fix{...}  projects remained after
removing projects that \Fix{...}. Table~\ref{tab:test-suites} shows
the JS sources we considered for each of these selected
projects..\Mar{identify the sources assoc. with the four analyzed
  engines. you said in the first sentence this is one source.} Overall, we found a total of \totfiles{} JS
files.\Mar{Briefly explain these sources.}

\begin{figure}[h]
  \centering
  \begin{lstlisting}
https://api.github.com/search/repositories?q=javascript-engine+stars:>=1000
  \end{lstlisting}
  \caption{\label{fig:query}
  Query to the GitHub API for JS engines projects that contain over 1K stars.\Fix{fix query}
  }
\end{figure}

@@

It is worth noting that some projects use distinct frameworks for
testing and require external libraries to run their testing
suites. For these projects, we needed to make small changes in the testing
infrastructure to be able to uniformly run tests in all
engines.\Mar{not entirely clear what you did to support
  this.$\rightarrow$}\Igor{wip}We aimed to use only the JS file with minor fixes
to support our environment. These fixes are composed by an assertion
function that throws an Error that we can capture by our
infraestruture.

>>>>

\subsection{Seed JS files\label{sec:seeds}}~We considered test suites
associated with all four JS engines we analyzed
(section~\ref{sec:methodology:engines}). In addition, we mined tests
from other GitHub repositories based on the following selection
criteria--the project must have received at least 1K stars and the
project must not use external libraries. Figure~\ref{fig:query}
illustrates the GitHub API query~\cite{github-rest-api} we used to
find javascript engines projects defined by the keyword
``javascript-engine''\Mar{is this a label or two keywords?}.  The
resulting list included a total of 33 projects.  A total of \Fix{4?}
projects remained after removing projects that \Fix{...}.\Mar{explique
como o numero baixou tanto.}

\begin{figure}[h]
  \centering
  \begin{lstlisting}
https://api.github.com/search/repositories?q=javascript-engine+stars:>=1000
  \end{lstlisting}
  \caption{\label{fig:query}
  Query used to find JS engine projects with over 1K stars.
  }
\end{figure}

Table~\ref{tab:test-suites} shows the JS sources we considered for
each of the selected projects.\Mar{identify the sources assoc. with
  the four analyzed engines. you said in the first sentence this is
  one source.}  Overall, we found a total of \totfiles{} JS
files.\Mar{Briefly explain these sources.} It is worth noting that some projects use distinct frameworks for
testing and require external libraries to run their testing
suites. For these projects, we needed to make small changes in the testing
infrastructure to be able to uniformly run tests in all
engines.\Mar{not entirely clear what you did to support
  this.$\rightarrow$}\Igor{wip}\Mar{apenas explique o que fez (mesmo
  que em portugues). isto
  nao deveria levar tempo que justifique escrever wip.}We aimed to use only the JS file with minor fixes
to support our environment. These fixes are composed by an assertion
function that throws an Error that we can capture by our
infraestruture.

@@
